---
title: "ClinGov Trials Data Explorer"
output:
  html_document:
    df_print: paged
---

```{r global-options}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=TRUE, cache.lazy = FALSE)
```

```{r}
library("dplyr")
library("DataExplorer")
library("ggplot2")
source("clingov_functions.R")
```
# Primary outcomes only
### Load data
```{r}
data <- read.delim("clingov_required_primary.tsv", header=T, stringsAsFactors=F, row.names=NULL, sep="\t")
#data <- read.delim("clingov_required.tsv", header=T, stringsAsFactors=F, row.names=NULL, sep="\t")
```

#How many unique studies in the required info data set?
```{r}
length(unique(published$nct_id))
```

#How many unique studies in the published data set?
```{r}
length(unique(data$nct_id))
```

### Introduce
```{r}
introduce(data)
```
### Plot Intro
```{r}
plot_intro(data)
```
### Plot missing
```{r}
plot_missing(data)
```
### Number of studies
```{r}
length(unique(data$nct_id))
```

### Plot barplot
```{r}
plot_bar(data)
```
### Plot histogram
```{r}
plot_histogram(data)
```

### Count number of primary and secondary outcomes by study
```{r}
outcome <- read.delim("outcome_add.tsv", header=T, stringsAsFactors=F, row.names=NULL, sep="\t")
outcome_primary <- outcome[outcome$outcome_type == "Primary",]
outcome_secondary <- outcome[outcome$outcome_type == "Secondary",]
primary_counts <- outcome_primary %>% count(nct_id)
secondary_counts <- outcome_secondary %>% count(nct_id)

ggplot(primary_counts, aes(n)) + geom_histogram(fill='darkblue') + scale_x_continuous(limits = c(0, 20)) + theme_Publication() + ggtitle("Number of primary outcomes per study")

ggplot(secondary_counts, aes(n)) + geom_histogram(fill='darkblue') + scale_x_continuous(limits = c(0, 40)) + theme_Publication() + ggtitle("Number of secondary outcomes per study")

```
### What are the top types of methods among our studies?
```{r}
data %>% count(method) %>% arrange(desc(n))
```
### What are the top types of estimates among our studies?
```{r}
data %>% count(param_type) %>% arrange(desc(n))
```

### Evaluate frequency of different intervention types in "required info" studies
```{r}
for_interv <- data %>% dplyr::select(nct_id, all_interv_types) %>% distinct()
interv_types <- c("Drug", "Other", "Biological", "Behavioral", "Device", "Procedure", "Dietary Supplement", "Radiation", "Diagnostic Test", "Genetic", "Combination Product")
for (i in interv_types) {
  print(i)
  temp <- dim(for_interv[grepl(i, for_interv$all_interv_types),])[1]
  print(temp)
}
```
### Evaluate frequency of different intervention types in "published" studies
```{r}
for_interv2 <- published %>% dplyr::select(nct_id, all_interv_types) %>% distinct()
for (i in interv_types) {
  print(i)
  temp <- dim(for_interv2[grepl(i, for_interv2$all_interv_types),])[1]
  print(temp)
}

```